N-Body problem

### 2014-09-13 article/article.tex
Changes ignore file and adds subheader for the literature study

\section{Introduction (phenomena)}
\section{Literature Study}
\section{Methodology}
\subsection{Discrete Approximation}
\subsection{Algorithms}
\subsection{Implementation}
\section{Experimental Results}
\section{Conclusions}

>>>>

\section{Introduction (phenomena)}
A world famous problem is the two body problem, most commonly known as the sun - earth problem.

\section{Literature Study}
background etc
\subsection{Newton's law}
\begin{equation}
 F = G\frac{m_1m_2}{r^2}
\end{equation}
With G as a gravitational constant and F as the force in Newton and $m_1,m_2$ the mass of the two systems in kg and $r$ is the distance between the center of the two bodies (see figure xx). 
Keplers problem? 
\subsection{Kepler}
Kepler problem, special case the Kepler orbit problem

\section{Methodology}
Newton's law, Kepler orbit for next position.

\subsection{Discrete Approximation}
Approximation of Newton's law, Kepler orbit. Possible accuracy problems, e.g. sensitivity analysis.

\subsection{Algorithms}

\subsection{Implementation}
\section{Experimental Results}
\section{Conclusions}
